%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed

%\DeclareMathOperator*{\argmin}{arg\,min}
%\DeclareMathOperator*{\argmax}{arg\,max}

\title{\LARGE \bf
Action Selection for Model Disambiguation
}


\author{P. Michael Furlong
\thanks{*This work was supported by LAKELANDER}% <-this % stops a space
\thanks{$^{1}$P. Michael Furlong is with NASA Ames Intelligent Robotics Group
        NASA Ames Research Center, Moffatt Field, CA 94035, USA
        {\tt\small padraig.m.furlong@nasa.gov}}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\textbf{TODO}

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

\begin{enumerate}
	\item Maximum Entropy sampling attempts to find the set of informative actionsabout a single distribution \textbf{cite}.  Likewise mutual information sampling attempts to select actions that are most informative about the parameters that an experimenter is trying to identify\textbf{cite}.  
	\item When there are multiple models to choose from we want to choose actions that are not only informative about that model, but also quickly help the decision maker choose \emph{between} the models.
\item Learning algorithms need to choose between models that represent the data
\item While learning it is important to economically spend sampling resources to disambiguate which models
\end{enumerate}

\section{BACKGROUND}

\begin{enumerate}
\item $A^2$ learner finds points where classifiers disagree.
\item UCB Improved uses bandit arms where their expected value overlaps
\item Maximum entropy sampling
\item Lindly 1956 defined a measure of how much a sample improves the certainty. 
\end{enumerate}

\section{MODEL SELECTION}

\begin{enumerate}
\item Bayesian Information Criterion
\item How to avoid overfitting?
\item Principled approach to actions that are most informative about the underlying model.
\end{enumerate}

\begin{equation} \label{eq:selection}
x = \arg\max_{x' \in S} H\left(K|\hat{f}\left(x'\right),x'\right) - H\left(K\right) \\
\end{equation}

However if we make the assumption that all values of $x$ are equally likely, then we can write the action selection as in Equation \ref{eq:selection-uniform}:

\begin{equation} \label{eq:selection-uniform}
x = \arg\max_{x' \in S} H\left(K|\hat{f}\left(x'\right)\right) - H\left(K\right)
\end{equation}


Where $K$ is the kernel and $x'$ is a point in the support of the function to be learned, $f\left(x\right)$

\begin{equation}
	\begin{aligned}
		H\left(K\right) &= \sum_{i}^{N} P\left(K_{i}\right)\log\left(P\left(K_{i}\right)\right) \\
	H\left(K|\hat{f}\left(x'\right)\right) &= \sum_{i}^{N} P\left(K_{i}|\hat{f}\left(x'\right)\right)\log\left(P\left(K_{i}|\hat{f}\left(x'\right)\right)\right) \\
		P\left(K_i|\hat{f}\left(x'\right)\right) &= \frac{P\left(K_i,\hat{f}\left(x'\right)\right)}{P\left(\hat{f}\left(x'\right)\right)} \\
		&= \frac{P\left(\hat{f}\left(x'\right)|K_i\right)P\left(K_i\right)}{P\left(\hat{f}\left(x'\right)\right)} \\
		&= \frac{P\left(\hat{f}\left(x'\right)|K_i\right)P\left(K_i\right)}{\sum_{j}^{N}P\left(\hat{f}\left(x'\right)|K_j\right)P(K_j)}
\end{aligned}
\end{equation}

If we were merely making observations and not taking actions, it would suffice to simply continually run a bayesian filter on the probability over each model.  However because the algorithm is trying to select actions that make the greatest reduction in uncertainty in the model, it may be different if each model were to be the correct one.  Therefore it is necessary to select an action as if each model were true, and then select from those maximally informative actions which one is likely to be most informative.  

When the true observation is made, the belief distribution over the models can be updated, which can then be used for selecting the next action.  

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

\section{EXPERIMENTS}

\begin{enumerate}
\item Restrict range of functions to $\left[0,1\right]$ (wlog)
\item Objective measure: Reconstruction error over the range finely sampled after the fact.
\item Initially start with a uniform prior over the models
\item With and without measurement noise.
\item Using Gaussian process regression \cite{bishop2006pattern} to represent the model selection 
\item Control algorithms: Random and uniform sampling, max entropy sampling over 
\item Stationary functions
\item Nonstationary functions
\end{enumerate}

\section{RESULTS}

plots
\begin{enumerate}
\item Reconstruction error vs number of samples for different strategies for stationary functions
\item Reconstruction error vs number of samples for different strategies for nonstationary functions
\item Time to compute action (on average) -- function of number of data points collected
\end{enumerate}


\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions. 

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGEMENT}

The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
